---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}

```

# pvbessmicrosimr

<!-- badges: start -->
<!-- badges: end -->

*pvbessmicrosimr* simulates the update of solar PV and battery-energy-storage-systems (BESS) by Irish households. 


It is based on household survey data collected in 2024. Micro-calibration of this model is done by *pvbesscalibrater. 

## Installation

You can install the latest version of *pvbessmicrosimr*:

```{r, eval=FALSE}
remotes::install_github("Phalacrocorax-gaimardi/pvbessmicrosimr")
```

## Basic Usage

The basic usage is:

```{r, eval=FALSE}
library(pvbessmicrosimr)
runABM(sD,Nrun=8,simulation_end=2030,use_parallel = T)
## basic example code
```
*sD* is a scenario datafile containing ~100 market, technical, policy and macro-calibration parameters

## Example






```{r cars}

```

## Analysis

```{r pressure, echo = FALSE}
```

